Parametricity for Primitive Nested Types and GADTs

### 2020-12-26 free-theorems-nesteds/20-mscs.tex
Repair proof of Prop 8.4

A third representation of left Kan extensions in locally presentable
categories is given in terms of colimits. Writing ${\mathcal C}_0$ for
the full subcategory of finitely presentable objects in the locally
presentable category $\mathcal C$, the left Kan extension can be
expressed as
\[
(\mathit{Lan}_{\ol K} F)\ol A \;=\; \colim{\ol{X : \,{\mathcal
        C}_0},\, \ol{f : K{\ol X} \to A}}{F \ol X}\]
Thus, if $F : \set^k \to \set$, $\ol{K} :
  \set^k \to \set^h$, $\ol{A} : \set^h$, and $\set_0$ is the full
  subcategory of finitely presentable objects in $\set$, --- i.e., is
  the category finite sets --- we  have that
\begin{equation}\label{eq:colim-form}
(\mathit{Lan}_K F) \ol{A} = \colim{\ol{S} : \set_0^k, \,\ol{f :
      K\ol{S} \to  A}}{F \ol{S}}
\end{equation}
If $\ol{S} : \set_0^k$ and $\ol{f : K\ol{S} \to A}$, let $j_{\ol{S},
  \ol{f}} : F \ol{S} \to (\mathit{Lan}_KF) \ol{A}$ be the morphism
indexed by $\ol{S}$ and $\ol{f}$ mapping the cocone into the colimit
in Equation~\ref{eq:colim-form}. Then for any $h$-tuple of functions
$\ol{g : A \to B}$, the functorial action $(\mathit{Lan}_K F) \ol{g}$
is the unique function from $(\mathit{Lan}_K F) \ol{A}$ to
$(\mathit{Lan}_K F) \ol{B}$ such that, for all $\ol{S} : \set^k_0$ and
$\ol{f : K\ol{S} \to A}$,\,
\begin{equation}\label{eq:cocone-def}
(\mathit{Lan}_KF) \ol{g} \circ j_{\ol{S},\, \ol{f}} = j_{\ol{S},\,
    \ol{g\, \circ f}}
  \end{equation}
holds.  We can similarly represent left Kan extensions of functors
over $\rel$ in terms of colimits. In that setting we will denote the
morphism mapping the cocone into the colimit $\iota$. We will make
good use of both of these representations in
Section~\ref{sec:term-sem} below.

@@

Of course, we intend to interpret $\Lan$-types as actual left Kan
extensions. To get started, we define their set and relational
interpretations to be
\[
  \setsem{\Gamma;\Phi \vdash
    (\Lan^{\ol{\alpha}}_{\ol{K}}\,F)\ol{A}}\rho = (\lambda \ol{S}.\,
  \textit{Lan}_{\ol{\setsem{\Gamma; \ol\alpha \vdash K}
      \rho[\ol{\alpha := S}]}}\, \setsem{\Gamma; \Phi, \ol\alpha
    \vdash F} \rho[\ol{\alpha := S}])\, \ol{\setsem{\Gamma; \Phi
      \vdash A}\rho}
\]
and

\[
  \relsem{\Gamma;\Phi \vdash
    (\Lan^{\ol{\alpha}}_{\ol{K}}\,F)\ol{A}}\rho = (\lambda \ol R.\,
    \textit{Lan}_{\ol{\relsem{\Gamma; \ol\alpha \vdash
          K}\rho[\ol{\alpha := R}]}}\, \relsem{\Gamma; \Phi, \ol\alpha
      \vdash F}\rho[\ol{\alpha := R}])\, \ol{\relsem{\Gamma; \Phi
        \vdash A}\rho}
\]

@@

\noindent
is defined to be 
\begin{multline*}
\big(\lambda \ol{S}.\,\textit{Lan}_{\ol{\setsem{\Gamma; \ol\alpha
      \vdash K}\rho[\ol{\alpha := S}]}}\,  
      \setsem{\Gamma; \Phi, \ol\alpha \vdash F}f[\ol{\alpha := \id_S}]\big)\,
    \ol{\setsem{\Gamma; \Phi \vdash A}\rho'} \\
\circ\;
  \big(\lambda \ol{S}.\,\textit{Lan}_{\ol{\setsem{\Gamma; \ol\alpha
        \vdash K}\rho[\ol{\alpha := S}]}}\,  
      \setsem{\Gamma; \Phi, \ol\alpha \vdash F}\rho[\ol{\alpha := S}]\big)\,
    \ol{\setsem{\Gamma; \Phi \vdash A}f}
\end{multline*}
or, equivalently by naturality,
\begin{multline*}
\big(\lambda \ol{S}.\,\textit{Lan}_{\ol{\setsem{\Gamma; \ol\alpha
      \vdash K}\rho[\ol{\alpha := S}]}}\, 
      \setsem{\Gamma; \Phi, \ol\alpha \vdash F}\rho'[\ol{\alpha := S}]\big)\,
    \ol{\setsem{\Gamma; \Phi \vdash A}f} \\
\circ\;
  \big(\lambda \ol{S}.\,\textit{Lan}_{\ol{\setsem{\Gamma; \ol\alpha
        \vdash K}\rho[\ol{\alpha := S}]}}\, 
      \setsem{\Gamma; \Phi, \ol\alpha \vdash F}f[\ol{\alpha := \id_S}]\big)\,
    \ol{\setsem{\Gamma; \Phi \vdash A}\rho}
\end{multline*}

@@

The problem in Example~\ref{ex:no-rel-transf} lies in the fact that
the {\color{red} functorial expression} along whose intepretation we
extend contains constants, i.e., {\color{red} subexpressions}
constructed from $\onet$. Indeed, if $\ol{\emptyset; \overline{\alpha}
  \vdash K}$ consists only of polynomial (i.e., sum-of-products)
expressions not containing constants (i.e., formed only from $+$,
$\times$, and the variables in $\alpha$), then
Lemma~\ref{lem:rel-transf-morph} actually does holds for $\Gamma; \Phi
\vdash (\Lan^{\alpha}_{\ol{K}} F)\ol{A}$. This is proved in

@@

When $i = 1$ we prove that
\[
\pi_1 \,( \relsem{ \Gamma; \Phi \vdash (\Lan^{\ol \alpha}_{\ol{K}}
  F)\ol{A} } \rho ) = \setsem{ \Gamma; \Phi \vdash (\Lan^{\ol
    \alpha}_{\ol{K}} F)\ol{A} } (\pi_1 \rho)
\]
by
providing a pair of inverse functions; the proof when $i=2$ is
entirely analogous. To this end, we define
\[
h : \pi_1\, ( \relsem{ \Gamma; \Phi \vdash (\Lan^{\ol \alpha}_{\ol{K}}
  F)\ol{A} } \rho ) \to \setsem{ \Gamma; \Phi \vdash (\Lan^{\ol
    \alpha}_{\ol{K}} F)\ol{A} } (\pi_1 \rho)
\]
to be the unique function given by the universal property of the
colimit representation of $h$'s domain. That is, we take $h$ to be the
unique morphism such that, for any $\ol{R : \rel_0}$ and $\ol{m :
  \relsem{ \emptyset; \ol\alpha \vdash K } \rho[\ol{\alpha := R}] \to
  \relsem{ \Gamma; \Phi \vdash A } \rho}$, we have $h \circ (\pi_1
\iota_{\ol{R},\, \ol{m}}) = j_{\ol{\pi_1 R}, \,\ol{\pi_1 m}}$.

@@

To see that $h$ and $k$ are mutually inverse we first observe that
\[
h \circ k \circ j_{\ol{S},\, \ol{f}}
= h \circ (\pi_1 \iota_{\ol{(S, 0, 0)}, \,\ol{(f, !)}})
= j_{\ol{\pi_1 (S, 0, 0)}, \,\ol{\pi_1 (f, !)}}
= j_{\ol{S},\, \ol{f}}
\]
for all $\ol{S : \set_0}$ and $\ol{f : \setsem{ \emptyset; \ol\alpha
    \vdash K } (\pi_1 \rho)[\ol{\alpha := S}] \to \setsem{ \Gamma;
    \Phi \vdash A } (\pi_1 \rho)}$, so that $h \circ k = \id$.
To see that  $k \circ h  = \id$ we first observe that
\[
k \circ h \circ (\pi_1 \iota_{\ol{R},\, \ol{m}}) = k \circ
j_{\ol{\pi_1 R}, \,\ol{\pi_1 m}} = \pi_1 \iota_{\ol{(\pi_1 R, 0,
    0)},\, \ol{(\pi_1 m, !)}}
\]
for all $\ol{R : \rel_0}$ and $\ol{m : \relsem{ \emptyset; \ol\alpha
    \vdash K } \rho[\ol{\alpha := R}] \to \relsem{ \Gamma; \Phi \vdash
    A } \rho}$. Then note that, for each sequence of morphisms
$\ol{(\id_{\pi_1 R}, !) : (\pi_1 R, 0, 0) \to R}$, we have that $\ol m
\,\circ\, \relsem{ \emptyset; \ol\alpha \vdash K } \rho[\ol{\alpha :=
    (\id_{\pi_1 R}, !)}] = (\ol{\pi_1 m}, !)$ in the indexing category
for the colimit representation of the codomain of $k$. This in turn
implies that {\color{red} $\iota_{\ol{R},\, \ol{m}} =
  \iota_{\ol{(\pi_1 R, 0, 0)},\, \ol{(\pi_1 m, !)}}$}, so that $k
\circ h \circ (\pi_1 \iota_{\ol{R},\, \ol{m}}) = \pi_1
\iota_{\ol{R},\, \ol{m}}$ for all $\ol R$ and $\ol m$, and thus $h
\circ k = \id$.

To prove Equation~\ref{eq:latter}, let $\iota$ be the cocone for the
colimit $\relsem{ \Gamma; \Phi \vdash (\Lan^{\ol \alpha}_{\ol{K}}
  F)\ol{A} } \rho$, let $j$ be the cocone for the colimit $\setsem{
  \Gamma; \Phi \vdash (\Lan^{\ol \alpha}_{\ol{K}} F)\ol{A} }
(\pi_i\rho)$, and let $h$ and $k$ be the isomorphisms showing that
$\pi_i(\setsem{ \Gamma; \Phi \vdash (\Lan^{\ol \alpha}_{\ol{K}}
  F)\ol{A} } \rho) = \setsem{ \Gamma; \Phi \vdash (\Lan^{\ol
    \alpha}_{\ol{K}} F)\ol{A} } (\pi_i\rho)$. Analogously, let
$\iota'$, $j'$, $h'$ and $k'$ be as above but for interpretations with
respect to $\rho'$ rather than $\rho$.  By definition, $\relsem{
  \Gamma; \Phi \vdash (\Lan^{\ol \alpha}_{\ol{K}} F)\ol{A} } f$ is the
unique morphism of relations such that, for any $\ol{R : \rel_0}$ and
$\ol{m : \relsem{ \emptyset; \ol\alpha \vdash K } \rho[\ol{\alpha :=
      R}] \to \relsem{ \Gamma; \Phi \vdash A } \rho}$,
\[
(\relsem{ \Gamma; \Phi \vdash (\Lan^{\ol \alpha}_{\ol{K}} F)\ol{A} }
f) \circ \iota_{\ol{R},\, \ol{m}} = \iota'_{\ol{R},\, \ol{\relsem{ \Gamma;
      \Phi \vdash A } f \, \circ\, m}}
\]
holds. Projecting onto the $i^{th}$ component of both sides thus gives
that
\[
\pi_i (\relsem{ \Gamma; \Phi \vdash (\Lan^{\ol \alpha}_{\ol{K}}
  F)\ol{A} } f) \circ \pi_i \iota_{\ol{R}, \,\ol{m}} = \pi_i
\iota'_{\ol{R},\, \ol{\relsem{ \Gamma; \Phi \vdash A } f \,\circ\, m}}
\]
Now, using the facts from above that $h \circ (\pi_i \iota_{\ol{R},
  \,\ol{m}}) = j_{\ol{\pi_i R},\, \ol{\pi_i m}}$ and, analogously,
that $h' \circ (\pi_i \iota'_{\ol{R},\, \ol{m}}) = j'_{\ol{\pi_i R},
  \,\ol{\pi_i m}}$, we get
{\color{red}
\[
\pi_i (\relsem{ \Gamma; \Phi \vdash (\Lan^{\ol \alpha}_{\ol{K}}
  F)\ol{A} } f) \circ k \circ j_{\ol{\pi_i R},\, \ol{\pi_i m}} = k'
\circ j'_{\ol{\pi_i R},\, \ol{\relsem{ \Gamma; \Phi \vdash A } (\pi_i f)
  \, \circ\, (\pi_i m)}}
\]
i.e., $\pi_i (\relsem{ \Gamma; \Phi \vdash (\Lan^{\ol \alpha}_{\ol{K}}
  F)\ol{A} } f)$ satisfies the universal property for $\setsem{
  \Gamma; \Phi \vdash (\Lan^{\ol \alpha}_{\ol{K}} F)\ol{A} } (\pi_i
f)$.} We therefore have that $\pi_i (\relsem{ \Gamma; \Phi \vdash
  (\Lan^{\ol \alpha}_{\ol{K}} F)\ol{A} } f) = \setsem{ \Gamma; \Phi
  \vdash (\Lan^{\ol \alpha}_{\ol{K}} F)\ol{A} } (\pi_i f)$ (up to
natural isomorphism) as desired.
\end{proof}

>>>>

A third representation of left Kan extensions in locally presentable
categories is given in terms of colimits. Writing ${\mathcal C}_0$ for
the full subcategory of finitely presentable objects in the locally
presentable category $\mathcal C$, the left Kan extension can be
expressed as
\[
(\mathit{Lan}_{\ol K} F)\ol A \;=\; \colim{\ol{X : \,{\mathcal
        C}_0},\, \ol{f : K{\ol X} \to A}}{F \ol X}\]
Thus, if $F : \set^k \to \set$, $\ol{K} :
  \set^k \to \set^h$, $\ol{A} : \set^h$, and $\set_0$ is the full
  subcategory of finitely presentable objects in $\set$, --- i.e., is
  the category finite sets --- we  have that
\begin{equation}\label{eq:colim-form}
(\mathit{Lan}_K F) \ol{A} = \colim{\ol{S} : \set_0^k, \,\ol{f :
      K\ol{S} \to  A}}{F \ol{S}}
\end{equation}
If $\ol{S} : \set_0^k$ and $\ol{f : K\ol{S} \to A}$, let $j_{\ol{S},
  \ol{f}} : F \ol{S} \to (\mathit{Lan}_KF) \ol{A}$ be the morphism
indexed by $\ol{S}$ and $\ol{f}$ mapping the cocone into the colimit
in Equation~\ref{eq:colim-form}.
%Then for any $h$-tuple of functions
%$\ol{g : A \to B}$, the functorial action $(\mathit{Lan}_K F) \ol{g}$
%is the unique function from $(\mathit{Lan}_K F) \ol{A}$ to
%$(\mathit{Lan}_K F) \ol{B}$ such that, for all $\ol{S} : \set^k_0$ and
%$\ol{f : K\ol{S} \to A}$,\,
%\begin{equation}\label{eq:cocone-def}
%(\mathit{Lan}_KF) \ol{g} \circ j_{\ol{S},\, \ol{f}} = j_{\ol{S},\,
%    \ol{g\, \circ f}}
%  \end{equation}
%holds, where
For any $h$-tuple of functions
$\ol{g : A \to B}$, the functorial action $(\mathit{Lan}_K F) \ol{g}$
is the unique function from $(\mathit{Lan}_K F) \ol{A}$ to
$(\mathit{Lan}_K F) \ol{B}$ such that, for all $\ol{S} : \set^k_0$ and
$\ol{f : K\ol{S} \to A}$,\,
\begin{equation}\label{eq:cocone-def}
(\mathit{Lan}_KF) \ol{g} \circ j_{\ol{S},\, \ol{f}}
= j'_{\ol{S},\, \ol{g\, \circ f}}
: F \ol{S} \to (\mathit{Lan}_KF) \ol{B}
\end{equation}
holds, where $j$ is the morphism mapping the cocone into
$(\mathit{Lan}_K F) \ol{A} = \colim{\ol{S} : \set_0^k, \,\ol{f :
    K\ol{S} \to A}}{F \ol{S}}$ and $j'$ is the morphism mapping the
cocone into $(\mathit{Lan}_K F) \ol{B} = \colim{\ol{S} : \set_0^k,
  \,\ol{f : K\ol{S} \to B}}{F \ol{S}}$.  Moreover, if $\alpha : F \to
F'$ is a natural transformation, then $\mathit{Lan}_K \alpha :
(\mathit{Lan}_K F) \to (\mathit{Lan}_K F')$ is defined to be the
induced natural transformation whose component $(\mathit{Lan}_K
\alpha) \ol{A} : (\mathit{Lan}_K F) \ol{A} \to (\mathit{Lan}_K F')
\ol{A}$ is the unique function such that $(\mathit{Lan}_K \alpha)
\ol{A} \,\circ\, j_{\ol{S}, \ol{f}} = j'_{\ol{S}, \ol{f}} \,\circ\,
\alpha_{\ol{S}}$. {\color{red} where $j$ is the cocone into
  $(\mathit{Lan}_K F) \ol{A}$ and $j'$ is the cocone into
  $(\mathit{Lan}_K F') \ol{A}$. REDUNDANT?} We can similarly
represent left Kan extensions of functors over $\rel$ in terms of
colimits. In that setting we will denote the morphism mapping the
cocone into the colimit $\iota$. We will make good use of both of
these representations in Section~\ref{sec:term-sem} below.

@@

Of course, we intend to interpret $\Lan$-types as actual left Kan
extensions. To get started, we define their set and relational
interpretations to be
\[
  \setsem{\Gamma;\Phi \vdash
    (\Lan^{\ol{\alpha}}_{\ol{K}}\,F)\ol{A}}\rho = (
  \textit{Lan}_{\lambda \ol{S}.\,\ol{\setsem{\Gamma; \ol\alpha \vdash K}
      \rho[\ol{\alpha := S}]}}\, \lambda \ol{S}.\,\setsem{\Gamma; \Phi, \ol\alpha
    \vdash F} \rho[\ol{\alpha := S}])\, \ol{\setsem{\Gamma; \Phi
      \vdash A}\rho}
\]
and

\[
  \relsem{\Gamma;\Phi \vdash
    (\Lan^{\ol{\alpha}}_{\ol{K}}\,F)\ol{A}}\rho = (
  \textit{Lan}_{\lambda \ol R.\,\ol{\relsem{\Gamma; \ol\alpha \vdash
        K}\rho[\ol{\alpha := R}]}}\, \lambda \ol R.\,\relsem{\Gamma;
    \Phi, \ol\alpha \vdash F}\rho[\ol{\alpha := R}])\,
  \ol{\relsem{\Gamma; \Phi \vdash A}\rho}
\]

@@

\noindent
is defined to be 
\begin{multline*}
\big(\textit{Lan}_{\lambda \ol{S}.\,\ol{\setsem{\Gamma; \ol\alpha
      \vdash K}\rho[\ol{\alpha := S}]}}\,  
      \lambda \ol{S}.\,\setsem{\Gamma; \Phi, \ol\alpha \vdash
        F}f[\ol{\alpha := \id_S}]\big)\, 
    \ol{\setsem{\Gamma; \Phi \vdash A}\rho'} \\
\circ\;
  \big(\textit{Lan}_{\lambda \ol{S}.\,\ol{\setsem{\Gamma; \ol\alpha
        \vdash K}\rho[\ol{\alpha := S}]}}\,  
      \lambda \ol{S}.\,\setsem{\Gamma; \Phi, \ol\alpha \vdash
        F}\rho[\ol{\alpha := S}]\big)\, 
    \ol{\setsem{\Gamma; \Phi \vdash A}f}
\end{multline*}
or, equivalently by naturality,
\begin{multline*}
\big(\textit{Lan}_{\lambda \ol{S}.\,\ol{\setsem{\Gamma; \ol\alpha
      \vdash K}\rho[\ol{\alpha := S}]}}\, 
      \lambda \ol{S}.\,\setsem{\Gamma; \Phi, \ol\alpha \vdash
        F}\rho'[\ol{\alpha := S}]\big)\, 
    \ol{\setsem{\Gamma; \Phi \vdash A}f} \\
\circ\;
  \big(\textit{Lan}_{\lambda \ol{S}.\,\ol{\setsem{\Gamma; \ol\alpha
        \vdash K}\rho[\ol{\alpha := S}]}}\, 
     \lambda \ol{S}.\, \setsem{\Gamma; \Phi, \ol\alpha \vdash
       F}f[\ol{\alpha := \id_S}]\big)\, 
    \ol{\setsem{\Gamma; \Phi \vdash A}\rho}
\end{multline*}

@@

The problem in Example~\ref{ex:no-rel-transf} lies in the fact that
the {\color{red} functorial expression} along whose intepretation we
extend contains constants, i.e., {\color{red} subexpressions}
constructed from $\onet$. Indeed, if $\ol{\emptyset; \overline{\alpha}
  \vdash K}$ consists only of polynomial (i.e., sum-of-products)
expressions not containing constants (i.e., formed only from $+$,
$\times$, and the variables in $\alpha$), then
Lemma~\ref{lem:rel-transf-morph} actually does holds for $\Gamma; \Phi
\vdash (\Lan^{\alpha}_{\ol{K}} F)\ol{A}$. This is proved in the
following proposition, which covers the case of
Lemma~\ref{lem:rel-transf-morph} for such $\Lan$-types.

@@

When $i = 1$ we prove that
\[
\pi_1 \,( \relsem{ \Gamma; \Phi \vdash (\Lan^{\ol \alpha}_{\ol{K}}
  F)\ol{A} } \rho ) = \setsem{ \Gamma; \Phi \vdash (\Lan^{\ol
    \alpha}_{\ol{K}} F)\ol{A} } (\pi_1 \rho)
\]
by
providing a pair of inverse functions; the proof when $i=2$ is
entirely analogous. To this end, we define
\[
h : \pi_1\, ( \relsem{ \Gamma; \Phi \vdash (\Lan^{\ol \alpha}_{\ol{K}}
  F)\ol{A} } \rho ) \to \setsem{ \Gamma; \Phi \vdash (\Lan^{\ol
    \alpha}_{\ol{K}} F)\ol{A} } (\pi_1 \rho)
\]
to be the unique function given by the universal property of the
colimit representation of $h$'s domain. That is, we take $h$ to be the
unique morphism such that, for any $\ol{R : \rel_0}$ and $\ol{m :
  \relsem{ \emptyset; \ol\alpha \vdash K } \rho[\ol{\alpha := R}] \to
  \relsem{ \Gamma; \Phi \vdash A } \rho}$, we have
\begin{equation}\label{eq:cocone-proj}
h \circ (\pi_1 \iota_{\ol{R},\, \ol{m}}) = j_{\ol{\pi_1 R},
  \,\ol{\pi_1 m}}
\end{equation}

@@

To see that $h$ and $k$ are mutually inverse we first observe that
\[
h \circ k \circ j_{\ol{S},\, \ol{f}}
= h \circ (\pi_1 \iota_{\ol{(S, 0, 0)}, \,\ol{(f, !)}})
= j_{\ol{\pi_1 (S, 0, 0)}, \,\ol{\pi_1 (f, !)}}
= j_{\ol{S},\, \ol{f}}
\]
for all $\ol{S : \set_0}$ and $\ol{f : \setsem{ \emptyset; \ol\alpha
    \vdash K } (\pi_1 \rho)[\ol{\alpha := S}] \to \setsem{ \Gamma;
    \Phi \vdash A } (\pi_1 \rho)}$, so that $h \circ k = \id$.
To see that  $k \circ h  = \id$ we first observe that
\begin{equation}\label{eq:k-comp-h}
k \circ h \circ (\pi_1 \iota_{\ol{R},\, \ol{m}}) = k \circ
j_{\ol{\pi_1 R}, \,\ol{\pi_1 m}} = \pi_1 \iota_{\ol{(\pi_1 R, 0,
    0)},\, \ol{(\pi_1 m, !)}}
\end{equation}
for all $\ol{R : \rel_0}$ and $\ol{m : \relsem{ \emptyset; \ol\alpha
    \vdash K } \rho[\ol{\alpha := R}] \to \relsem{ \Gamma; \Phi \vdash
    A } \rho}$. Then note that, for each sequence of morphisms
$\ol{(\id_{\pi_1 R}, !) : (\pi_1 R, 0, 0) \to R}$, we have that
\[\ol{m
\,\circ\, \relsem{ \emptyset; \ol\alpha \vdash K } \id_\rho[\ol{\alpha
    := (\id_{\pi_1 R}, !)}] = (\pi_1 m, !)}\]
in the indexing category for the colimit representation of the
codomain of $k$. This implies that
\[\iota_{\ol{R},\, \ol{m}} \,\circ\, \relsem{ \Gamma; \Phi,
  \ol\alpha \vdash F } \id_{\rho}[\ol{\alpha := (\id_{\pi_1 R}, !)}]
= \iota_{\ol{(\pi_1 R, 0, 0)},\, \ol{(\pi_1 m, !)}}\] Projecting the
first component thus gives
\[(\pi_1 \iota_{\ol{R},\,
  \ol{m}}) \, \circ\, \pi_1 ( \relsem{ \Gamma; \Phi, \ol\alpha \vdash
  F } \id_{\rho}[\ol{\alpha := (\id_{\pi_1 R}, !)}]) = \pi_1
\iota_{\ol{(\pi_1 R, 0, 0)},\, \ol{(\pi_1 m, !)}}\]
Now, the induction hypothesis on $\Gamma;\Phi,\ol\alpha
\vdash F$ gives that
\[\begin{array}{lll}
 &  & \pi_1 ( \relsem{ \Gamma; \Phi, \ol\alpha \vdash F}
\id_{\rho}[\ol{\alpha := (\id_{\pi_1 R}, !)}])\\
& = & \setsem{ \Gamma; \Phi, \ol\alpha \vdash F } \id_{\pi_1
  \rho}[\ol{\alpha := \id_{\pi_1 R}}]\\
& = & \id_{\setsem{ \Gamma; \Phi, \ol\alpha \vdash F } (\pi_1
  \rho)[\ol{\alpha := \pi_1 R}]}
\end{array}\]
so that, in fact, $\pi_1 \iota_{\ol R,\,\ol m} =
\pi_1\iota_{\ol{(\pi_1 R, 0, 0)},\, \ol{(\pi_1 m, !)}}$.  Finally, by
Equation~\ref{eq:k-comp-h} we have $k \circ h \circ (\pi_1
\iota_{\ol{R},\, \ol{m}}) = \pi_1 \iota_{\ol{(\pi_1 R, 0, 0)},\,
  \ol{(\pi_1 m, !)}}  = \pi_1 \iota_{\ol{R},\, \ol{m}}$ for all $\ol
R$ and $\ol m$, and thus $k \circ h = \id$.

To prove Equation~\ref{eq:latter}, first recall that
$\relsem{ \Gamma; \Phi \vdash (\Lan^{\ol \alpha}_{\ol{K}} F)\ol{A} }
f$ is defined to be
\begin{multline*}
\big(\textit{Lan}_{\ol{\lambda \ol{R}.\,\relsem{\Gamma; \ol\alpha
      \vdash K}\rho[\ol{\alpha := R}]}}\, \lambda
\ol{R}.\,\relsem{\Gamma; \Phi, \ol\alpha \vdash F}f[\ol{\alpha :=
    \id_R}]\big)\, \ol{\relsem{\Gamma; \Phi \vdash A}\rho'} \\ \circ\;
\big(\textit{Lan}_{\ol{\lambda \ol{R}.\,\relsem{\Gamma; \ol\alpha
      \vdash K}\rho[\ol{\alpha := R}]}}\, \lambda
\ol{R}.\,\relsem{\Gamma; \Phi, \ol\alpha \vdash F}\rho[\ol{\alpha :=
    R}]\big)\, \ol{\relsem{\Gamma; \Phi \vdash A}f}
\end{multline*}
and $\setsem{\Gamma; \Phi \vdash (\Lan^{\ol \alpha}_{\ol{K}} F)\ol{A}
} (\pi_i f)$ is defined to be
\begin{multline*}
\big(\textit{Lan}_{\ol{\lambda \ol{S}.\,\setsem{\Gamma; \ol\alpha
      \vdash K}(\pi_i \rho)[\ol{\alpha := S}]}}\, \lambda
\ol{S}.\,\setsem{\Gamma; \Phi, \ol\alpha \vdash F}(\pi_i f)[\ol{\alpha
    := \id_S}]\big)\, \ol{\setsem{\Gamma; \Phi \vdash A}(\pi_i
  \rho')}\\ \circ\; \big(\textit{Lan}_{\ol{\lambda
    \ol{S}.\,\setsem{\Gamma; \ol\alpha \vdash K}(\pi_i
    \rho)[\ol{\alpha := S}]}}\, \lambda \ol{S}.\,\setsem{\Gamma; \Phi,
  \ol\alpha \vdash F}(\pi_i \rho)[\ol{\alpha := S}]\big)\,
\ol{\relsem{\Gamma; \Phi \vdash A}(\pi_i f)}
\end{multline*}
It therefore suffices to show that
\begin{multline}\label{eq:part-one}
\pi_i \Big( \big(\textit{Lan}_{\ol{\lambda \ol{R}.\,\relsem{\Gamma; \ol\alpha
      \vdash K}\rho[\ol{\alpha := R}]}}\,  
      \lambda \ol{R}.\,\relsem{\Gamma; \Phi, \ol\alpha \vdash F}f[\ol{\alpha := \id_R}]\big)\,
    \ol{\relsem{\Gamma; \Phi \vdash A}\rho'} \Big) \\
= \big(\textit{Lan}_{\ol{\lambda \ol{S}.\,\setsem{\Gamma; \ol\alpha
      \vdash K} (\pi_1 \rho) [\ol{\alpha := S}]}}\,  
      \lambda \ol{S}.\,\setsem{\Gamma; \Phi, \ol\alpha \vdash F}(\pi_i f)[\ol{\alpha := \id_S}]\big)\,
    \ol{\setsem{\Gamma; \Phi \vdash A}(\pi_i \rho')}
\end{multline}
and that
\begin{multline}\label{eq:part-two}
\pi_i \Big( \big(\textit{Lan}_{\ol{\lambda \ol{R}.\,\relsem{\Gamma; \ol\alpha
        \vdash K}\rho[\ol{\alpha := R}]}}\,  
      \lambda \ol{R}.\,\relsem{\Gamma; \Phi, \ol\alpha \vdash F}\rho[\ol{\alpha := R}]\big)\,
    \ol{\relsem{\Gamma; \Phi \vdash A}f} \Big) \\
= \big(\textit{Lan}_{\ol{\lambda \ol{S}.\,\setsem{\Gamma; \ol\alpha
        \vdash K} (\pi_i \rho) [\ol{\alpha := S}]}}\,  
      \lambda \ol{S}.\,\setsem{\Gamma; \Phi, \ol\alpha \vdash F} (\pi_i \rho) [\ol{\alpha := S}]\big)\,
    \ol{\setsem{\Gamma; \Phi \vdash A} (\pi_i f)}
\end{multline}

To prove Equation~\ref{eq:part-one} we first observe that
  the universal property (Equation~\ref{eq:cocone-def}) of
\big(\textit{Lan}_{\ol{\lambda \ol{R}.\,\relsem{\Gamma; \ol\alpha
      \vdash K}\rho[\ol{\alpha := R}]}}\, \lambda
\ol{R}.\,\relsem{\Gamma; \Phi, \ol\alpha \vdash F}f[\ol{\alpha :=
    \id_R}]\big)\, \ol{\relsem{\Gamma; \Phi \vdash A}\rho'}
gives that, for all $\ol{R : \rel_0}$ and $\ol{m : \relsem{\Gamma;
    \ol\alpha \vdash K}\rho[\ol{\alpha := R}] \to \relsem{\Gamma; \Phi
    \vdash A}\rho'}$,
& & \big(\textit{Lan}_{\ol{\lambda \ol{R}.\,\relsem{\Gamma; \ol\alpha
      \vdash K}\rho[\ol{\alpha := R}]}}\, \lambda
\ol{R}.\,\relsem{\Gamma; \Phi, \ol\alpha \vdash F}f[\ol{\alpha :=
    \id_R}]\big)\, \ol{\relsem{\Gamma; \Phi \vdash A}\rho'} \,\circ\,
\iota_{\ol{R}, \ol{m}}\\[2ex]
& = & \iota'_{\ol{R}, \ol{m}} \,\circ\, \relsem{\Gamma; \Phi,
  \ol\alpha \vdash F}f[\ol{\alpha := \id_R}]
Here, $\iota$ is the morphism mapping the cocone into the colimit
\big(\textit{Lan}_{\ol{\lambda \ol{R}.\,\relsem{\Gamma; \ol\alpha
      \vdash K}\rho[\ol{\alpha := R}]}}\, \lambda
\ol{R}.\,\relsem{\Gamma; \Phi, \ol\alpha \vdash F}\rho[\ol{\alpha :=
    R}]\big)\, \ol{\relsem{\Gamma; \Phi \vdash A}\rho'}
and $\iota'$ is the morphism mapping the cocone into the colimit
\big(\textit{Lan}_{\ol{\lambda \ol{R}.\,\relsem{\Gamma; \ol\alpha
      \vdash K}\rho[\ol{\alpha := R}]}}\, \lambda
\ol{R}.\,\relsem{\Gamma; \Phi, \ol\alpha \vdash F}\rho'[\ol{\alpha :=
    R}]\big)\, \ol{\relsem{\Gamma; \Phi \vdash A}\rho'}
Projecting, together with the induction hypothesis for $\Gamma; \Phi,
\ol\alpha\vdash F$, thus gives
 & & \pi_i \Big( \big(\textit{Lan}_{\ol{\lambda \ol{R}.\,\relsem{\Gamma;
      \ol\alpha \vdash K}\rho[\ol{\alpha := R}]}}\, \lambda
\ol{R}.\,\relsem{\Gamma; \Phi, \ol\alpha \vdash F}f[\ol{\alpha :=
    \id_R}]\big)\, \ol{\relsem{\Gamma; \Phi \vdash A}\rho'} \Big)
\,\circ\, \pi_i \iota_{\ol{R}, \ol{m}} \\[2ex]
& = & \pi_i \iota'_{\ol{R},
  \ol{m}} \,\circ\, \setsem{\Gamma; \Phi, \ol\alpha \vdash F} (\pi_i
f)[\ol{\alpha := \id_{\pi_i R}}]
Equation~\ref{eq:cocone-proj} {\color{red} and its analogue for
  $\iota'$ and $j'$ then give --- HOW?????}
 & & \pi_i \Big( \big(\textit{Lan}_{\ol{\lambda
    \ol{R}.\,\relsem{\Gamma; \ol\alpha \vdash K}\rho[\ol{\alpha :=
        R}]}}\, \lambda \ol{R}.\,\relsem{\Gamma; \Phi, \ol\alpha
  \vdash F}f[\ol{\alpha := \id_R}]\big)\, \ol{\relsem{\Gamma; \Phi
    \vdash A}\rho'} \Big) \,\circ\, {\color{red} j?}f_{\ol{\pi_i R},
  \ol{\pi_i m}} \\[2ex]
& = & j'_{\ol{\pi_i R}, \ol{\pi_i m}} \,\circ\, \setsem{\Gamma; \Phi,
      \ol\alpha \vdash F} (\pi_i f)[\ol{\alpha := \id_{\pi_i R}}]
where $j$ is the morphism mapping the cocone into the colimit
\big(\textit{Lan}_{\ol{\lambda \ol{S}.\,\setsem{\Gamma; \ol\alpha
      \vdash K}(\pi_i \rho)[\ol{\alpha := S}]}}\, \lambda
\ol{S}.\,\setsem{\Gamma; \Phi, \ol\alpha \vdash F}(\pi_i
\rho)[\ol{\alpha := S}]\big)\, \ol{\setsem{\Gamma; \Phi \vdash
    A}(\pi_i \rho')}
and $j'$ is the morphism mapping the cocone into the colimit
\big(\textit{Lan}_{\ol{\lambda \ol{S}.\,\setsem{\Gamma; \ol\alpha
      \vdash K}\rho[\ol{\alpha := S}]}}\, \lambda
\ol{R}.\,\setsem{\Gamma; \Phi, \ol\alpha \vdash F}(\pi_i
\rho')[\ol{\alpha := S}]\big)\, \ol{\setsem{\Gamma; \Phi \vdash
    A}(\pi_i \rho')}
By the surjectivity of each $\pi_i : \rel \to \set$ we have that
